---
title: "exercicio-1"
format: html
editor: visual
---

## Exercise 1

Let’s start really easy (don’t worry, we’ll quickly move to more challenging problems) with a vector containing just a single number, which we also call a scalar. Enter a vector in R, by just typing a random number, e.g. `100`, at the prompt and hit the Enter key.

```{r}
100
```

### Exercise 2

Great! You just created your first vector! Now, let’s first enter a vector with more than one number. E.g. a vector containing the numbers 1, 2, 3, 4, 5, in that order. If you enter these numbers just like this, R will respond with an error message. It throws an error, because it needs a little bit more information from our side that we actually want to store those numbers in a vector structure. We have to use the following notation for this:

`c(1, 2, 3, 4, 5)`.

Now, enter a vector with the first 5 even numbers in R, and hit Enter.

```{r}
c(2, 4, 6, 8, 10)
```

### Exercise 3

Let’s now enter a much longer vector, containing the numbers 1 to 10, 10 times (use copy & paste). What do the numbers between square brackets in the R output mean?

```{r}
c(1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10,
  1,2,3,4,5,6,7,8,9,10)
```

### Exercise 4

You should be pretty familiar with entering vectors now. You might actually feel a little *bored* by typing all these numbers. Life would be pretty miserable if we would have to enter data this way over and over again in R. But fortunately, there is a neat solution! We can *assign* a vector to a variable name such that we can retrieve the data we have entered, conveniently by just typing the name of the variable.

Try to assign a vector containing the numbers 1, 2, 3, 4, 5 to a variable named `a`, using the assignment operator (`<-`), and see which of the statements below work.

Enter each of the 9 statements one at a time at the prompt, hit Enter, and try to retrieve the contents of `a`, by typing `a` at the prompt after you entered each statement:

1.  `a<-c(1, 2, 3, 4, 5)`

2.  `a <- c(50, 60, 70, 80, 90)`

3.  `a -> c(20, 31, 42, 53, 64)`

4.  `c(5, 6, 7, 9, 10) <- a`

5.  `c(101, 102, 103, 104, 105) -> a`

6.  `a < - c(11, 12, 13, 14, 15)`

7.  `a < -c(100, 99, 88, 77, 66)`

8.  `assign(a, c(1000, 2000, 3000, 4000, 5000))`

9.  `assign('a', c(83, 16, 35, 58, 3))`

```{r}
a<-c(1, 2, 3, 4, 5)
a
```

```{r}
a <- c(50, 60, 70, 80, 90)
a
```

```{r}
a -> c(20, 31, 42, 53, 64) #ERRO
```

```{r}
c(5, 6, 7, 9, 10) <- a #ERRO
```

```{r}
c(101, 102, 103, 104, 105) -> a
a
```

```{r}
a < - c(11, 12, 13, 14, 15)
```

```{r}
a < -c(100, 99, 88, 77, 66)
```

```{r}
assign(a, c(1000, 2000, 3000, 4000, 5000))
```

```{r}
assign('a', c(83, 16, 35, 58, 3))
a
```

### Exercise 5

In an R script, you might have created dozens or even hundreds of vectors. In that case, naming them `a`, `b`, `c` etc. is not ideal, because it will be difficult to keep track of what all those letters actually mean. This problem is easily mitigated by using longer, and meaningful, variable names.

Assign the following vectors to a meaningful variable name:

1.  `c(2, 4, 6, 8, 10, 12, 14, 16, 20)`

2.  `0`

3.  `3.141593`

4.  `c(1, 10, 100, 1000, 10000, 100000)`

```{r}
vector1 <- c(2, 4, 6, 8, 10, 12, 14, 16, 20)
vector1
```

```{r}
zero = 0
zero
```

```{r}
pi_ <- 3.141593
pi_
```

```{r}
vector2 <- c(1, 10, 100, 1000, 10000, 100000)
vector2
```

### Exercise 6

Create vectors that correspond to the following variables names:

1.  bmi

2.  age

3.  daysPerMonth

4.  firstFivePrimeNumbers

```{r}
bmi <- c(2, 5, 6)
bmi
```

```{r}
age <- 33
age
```

```{r}
daysPerMonth <- 30
daysPerMonth
```

```{r}
firstFivePrimeNumbers <- c(2,3,5,7,11)
firstFivePrimeNumbers
```

### Exercise 7

So far, we have created vectors from a bunch of numbers. Instead of numbers, however, you can also enter other vectors, e.g. `c(vector1, vector2, vector3)`, and string them together.

To practise this, let’s first create three vectors that each contain just 1 element with variable names `p`, `q`, and `r`, and values 1, 2, and 3. Then, create a new vector that contains multiple elements, using the scalars we just created. I.e., create a vector `u` of length 3, with the subsequent elements of `p`, `q` and `r`.

```{r}
p = (1)
q = (2)
r = (3)
u = c(p,q,r)
u
```

### Exercise 8

To play with this a little more, let’s create a longer vector, using only the assignment operator (`<-`), the `c()` function, and the vector `u` we just created. I.e., create a new vector `u` with length 96 that contains the elements of `u` as follows: 1, 2, 3, 1, 2, 3, …., 1, 2, 3

```{r}
u <- c(1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3,
       1,2,3)
u
```
